---
title: "存活分析 作業2"
author: "孫浩哲 M072040002"
date: "2019年5月23日"
output: word_document
---
##1.

#(1)
```{r}
require(KMsurv)
require(survival)
require(dplyr)
require(survminer)
data(bmt)
fitmo=survfit(Surv(t2,d3)~factor(group),data=bmt)
plot(fitmo,col=c("red","gold","green"),xlab="time",ylab="K-M survival function")
legend("topright", legend = c("all", "low-risk", "high-risk"),col=c("red","gold","green"),text.col=c("red","gold","green"))
```

The disease-free survival functions for the three populations are not same.

#(2)

$H_{0}$：All hazard functions are same. $H_{a}$：At least one hazard is different.

```{r}
fitt=survdiff(Surv(t2,d3)~factor(group),data=bmt)
fitt
```

We reject the $H_{0}$, that is, at least one hazard is different.

#(3)

```{r}
fit3=survdiff(Surv(t2,d3)~factor(group),data=bmt,rho=1)
fit3
```
Under $\alpha=0.05$, the test statistic is $13.8$ and the rejection  region is  $\chi_{2}^2=5.99146$ .¶

Since $13.8≥χ22=5.99146$, we reject the null hypothesis.

##2.

#(1)
```{r}
data(bfeed)
fit_model = coxph(Surv(duration,delta)~yschool+factor(poverty)+factor(race),data=bfeed)
fit_model %>% coef
fit_model %>% confint(level=0.99)
```

#(2)

The risk will decrease $e^{0.05}\approx0.951$ years if the mother's years of school increases one year.

#(3)

```{r}
summary(fit_model)->summ
summ$coefficients
exp(confint(fit_model,level=0.99))
```
The RR is $0.8262$ and the 99%CI is $[0.652,1.048]$.

#(4)

```{r}
fit_model$var
sd = sqrt(0.0106+0.0089-2*0.0017) # Var(X-Y) = Var(X)+Var(Y)-2Cov(X,Y)
ans = 0.1322-0.2286+c(-qnorm(0.995),qnorm(0.995))*sd
ans %>% exp
```

By the result we get in (3), the RR $1.1413305/1.2568691\approx0.91$.

The CI of RR is $[0.655,1.259]$

#(5)

$H_{0}$：all coefficients of race are 0 $H_{a}$：at least one of coefficient of race are not 0.

rejection region: ${\chi^2_{SC}>5.99}$ 

```{r}
##wald test
beta1hat=fit_model$coefficients[3:4]
var11=fit_model$var[3:4,3:4]
chi=(beta1hat %>% t)%*%solve(var11)%*% beta1hat # test-statistic
1-pchisq(chi,2) #chi-square distribution with df 2
```

```{r}
##likelihood ratio test
fit_model.reduced=coxph(Surv(duration,delta)~yschool+factor(poverty),data=bfeed)
LR=2*(fit_model$loglik[2]-fit_model.reduced$loglik[2]) # test-statistic
1-pchisq(LR,2) #chi-square distribution with df 2
```

```{r}
##score test
fit0=coxph(Surv(duration,delta)~yschool+factor(poverty)+factor(race),data=bfeed,init=c(fit_model.reduced$coefficients,0,0),iter=0)
score.vector=colSums(coxph.detail(fit0)$score)
chiSC=t(score.vector[3:4]%*%fit0$var[3:4,3:4]%*%score.vector[3:4]) 
# test-statistic
1-pchisq(chiSC,2) #chi-square distribution with df 2
qchisq(0.95,2)
```
No matter Wald test, likelihood ratio test and score test, we can reject the $H_{0}$, that is, we accept at least one of coefficient of race are not 0.