---
title: "Survival analysis HW 1"
author: "孫浩哲 M072040002"
date: "2019年3月26日"
output: word_document
---
```{r}
library(KMsurv)
library(survival)
library(ciTools)
data(bfeed)
{
bfeed$white=0
bfeed$white[which(bfeed$race==1)]=1
bfeed$black=0
bfeed$black[which(bfeed$race==2)]=1
bfeed$other=0
bfeed$other[which(bfeed$race==3)]=1
}
```

```{r}
#############
model=survreg(Surv(duration)~poverty+yschool+white+black+other,data=bfeed,dist="weibull")
```

##第1題
```{r}
summary(model)
```
$$Y=\ln{X}=2.1093+0.1878\times poverty+0.0344\times yschool+0.2545\times white+0.1183\times black+1.03*W$$

##第2題

```{r}
coef(model)
```
If mother's years of school increases one year,the mean log survival time will increases $0.0343$ weeks.

##第3題

```{r}
summary(model)
```
The poverty has significant effect of breast feeding.

##第4題

The mother's education level has no significant effect of breast feeding.

##第5題
```{r}
msu=add_ci(bfeed,model, alpha = 0.1, names = NULL, yhatName = "mean_pred")
meansurvival=mean(msu$mean_pred)
mediansurvival=median(msu$mean_pred)
c(meansurvival,mediansurvival)
```
The mean of survival time is $16.16437$, and median of survival time is $16.29467$.

##第6題

```{r}
red=survreg(Surv(duration)~poverty+yschool,data=bfeed,dist="weibull")
anova(red,model)
```
The mother's race has no significant effect of breast feeding.

##第7題

```{r}
confint(model)
```
The $95\%$ confidence interval for the regression coefficient for poverty is $[\ 0.0043,0.3713\ ]$
